Globally-centered autocovariances in MCMC

### 2020-07-19 Paper/main.tex
Pushing reorganized setup.

@@

A rough outline of the organization
\begin{enumerate}
  \item Introduction, with a sneak peak at new plots. Change this example to a univariate mixture of Gaussians.

@@

    Describe MC averages and CLT
    \begin{itemize}
      \item Globally-centered Spectral variance estimators
      \begin{itemize}
        \item Theoretical results
        \item Computational gains
      \end{itemize}
      \item Explore: Charlie's initial sequence estimators
    \end{itemize}

@@

@@

\begin{example}[Motivating example]
  gj
\begin{figure}
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{plots/acf,n=500.pdf}
  \caption{$n = 500$}
  \label{subfig:acf-500}
\end{subfigure}\\
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{plots/acf,n=10000.pdf} 
  \caption{$n = 10^4$}
  \label{subfig:acf-5e4}
\end{subfigure}
\caption{Autocorrelation plot for ACF and R-ACF for first chain out of two parallel Markov chains. First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n =  10^4$, converged}
\label{fig:var_acf_ccf}
\end{figure}

@@

@@

@@

\subsection{Average Spectral Variance } \label{sec:asv}

Recall that for $s^{th}$ Markov chain, the spectral variance estimator is given by,

\begin{align*}
    \hat{\Sigma}_{SV,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)\\
    \hat{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T
\end{align*}

The average spectral variance ($\Sigma_{ASV}$) is computed by averaging the SV estimates from all $m$ Markov chains.

\[
\hat{\Sigma}_{ASV} = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{SV,s}
\]

\subsection{Replicated Spectral Variance } \label{sec:rsv}

@@

@@

>>>>

  \item The contents are a bit messy right now, and I am having trouble organizing my thoughts.

@@

A rough outline of the organization
\begin{enumerate}
  \item Introduction, with a sneak peak at new plots. Change this example to a univariate mixture of Gaussians.:

    Here, we will just explain the problem with the old ACF and what happens by using the new ACF. We will show a plot to illustrate the impact. Then we will summarize the three places this will have an impact: (1) ACF plots (2) estimators of the asymptotic variance-covariance matrix (3) estimating effective sample size.

@@

    Describe MC averages and CLT here and not before
    \begin{itemize}
      \item Globally-centered Spectral variance estimators
      \begin{itemize}
        \item Theoretical results
        \item Fast implementation
      \end{itemize}
    \end{itemize}

@@

  \item Discussion
    \begin{itemize}
      \item All plots have been made using the package:(name). The package can be found on GitHub.
      \item One thing to discuss is that the new autocovariances can be used in the initial sequence estimators as well.
    \end{itemize}

@@

{\color{blue} Dootika: The introduction above needs some rewrite based on my pointers in blue above. We should introduce the definition of autocovariance here and present the old and the new estimators of $\Gamma$ here. So take some of the details out of the next section and put them here.}

\begin{example}[Demonstrative example]

We demonstrate the striking difference in the ACF plots through mixture of Gaussian target density using a random-walk Metropolis-Hastings sampler.

{\color{blue} Dootika: add new plots here when available for this target density. }
% \begin{figure}
% \begin{subfigure}{\textwidth}
%   \centering
%   \includegraphics[width=.8\linewidth]{plots/acf,n=500.pdf}
%   \caption{$n = 500$}
%   \label{subfig:acf-500}
% \end{subfigure}\\
% \begin{subfigure}{\textwidth}
%   \centering
%   \includegraphics[width=.8\linewidth]{plots/acf,n=10000.pdf} 
%   \caption{$n = 10^4$}
%   \label{subfig:acf-5e4}
% \end{subfigure}
% \caption{Autocorrelation plot for ACF and R-ACF for first chain out of two parallel Markov chains. First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n =  10^4$, converged}
% \label{fig:var_acf_ccf}
% \end{figure}

@@

\subsection{Theoretical results} % (fold)
\label{sub:theoretical_results}

% subsection theoretical_results (end)

@@

{\color{blue}Dootika: this section here needs to be much tighter in its presentation. We will need to remember that the paper is no longer about the SV estimators but about autocorrelations. So will have to present the discussion similarly. }

\subsection{Globally-centered spectral variance estimators} % (fold)
\label{sub:globally_centered_spectral_variance_estimators}

% subsection globally_centered_spectral_variance_estimators (end)

@@

% \subsection{Average Spectral Variance } \label{sec:asv}

% Recall that for $s^{th}$ Markov chain, the spectral variance estimator is given by,

% \begin{align*}
%     \hat{\Sigma}_{SV,s} &= \sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\hat{\Gamma}_s(k)\\
%     \hat{\Gamma}_s(k) &= \dfrac{1}{n}\sum_{t=1}^{n-k}(X_{st}-\overline{X_s})(X_{s(t+k)}-\overline{X_s})^T
% \end{align*}

% The average spectral variance ($\Sigma_{ASV}$) is computed by averaging the SV estimates from all $m$ Markov chains.

% \[
% \hat{\Sigma}_{ASV} = \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Sigma}_{SV,s}
% \]

@@

\subsubsection{Theoretical results} \label{sec:rsv}

@@

\subsubsection{Fast implementation} % (fold)
\label{ssub:fast_implementation}

% subsubsection fast_implementation (end)
